Random Forest

### 2021-05-14 RandomForestKeogh.Rmd
adding roc and other metrics

```{r}
library(randomForest)
library(rio)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(DT)
library(plotly)
```

@@

## Largest Model
```{r}

# create predictions
large_predict = predict(
  stroke_rf,
  stroke_factor_testing_data,
  type="response",
  predict.all = TRUE,
  proximity = TRUE
)

## Smaller Tree Model
```{r}
smaller_predict = predict(
  stroke_rf_4,
  stroke_factor_testing_data,
  type="response",
  predict.all = TRUE,
  proximity = TRUE
)
```

## Lean Model
```{r}
lean_predict = predict(
  stroke_rf_lean,
  stroke_factor_testing_data_lean,
  type="response",
  predict.all = TRUE,
  proximity = TRUE
)
```

## Aggregate Data
```{r}

# combine all predictions
predictions = data.frame(
  stroke_factor_testing_data$stroke,
  large_predict$predicted$aggregate,
  smaller_predict$predicted$aggregate,
  lean_predict$predicted$aggregate
)

@@

@@

## Confusion Matrix
```{r}
table(predictions$Reference, predictions$`Large Prediction`)
table(predictions$Reference, predictions$`Small Prediction`)
table(predictions$Reference, predictions$`Lean Prediction`)

@@

Y axis is ground truth, x axis is predictions

@@

>>>>

```{r}
library(randomForest)
library(rio)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(DT)
library(plotly)
library(caret)
```

@@

```{r}
# create predictions
large_predict = predict(
  stroke_rf,
  stroke_factor_testing_data,
  type="response",
  predict.all = TRUE,
  proximity = TRUE
)

# create predictions
smaller_predict = predict(
  stroke_rf_4,
  stroke_factor_testing_data,
  type="response",
  predict.all = TRUE,
  proximity = TRUE
)

# create predictions
lean_predict = predict(
  stroke_rf_lean,
  stroke_factor_testing_data_lean,
  type="response",
  predict.all = TRUE,
  proximity = TRUE
)
```

```{r}
# combine all predictions
predictions = data.frame(
  as.factor(stroke_factor_testing_data$stroke),
  as.factor(large_predict$predicted$aggregate),
  as.factor(smaller_predict$predicted$aggregate),
  as.factor(lean_predict$predicted$aggregate)
)

@@

plt = predictions %>%
  ggplot(
    aes(
      x=as.numeric(row.names(predictions)),
      y=`Stroke Ground Truth`,
      color="black"
    )
  )+
  geom_point()+
  geom_point(
    aes(
      y=`Large Prediction`,
      color='red'
    ),
  )+
  geom_point(
    aes(
      y=`Small Prediction`,
      color='blue'
    ),
  )+
  geom_point(
    aes(
      y=`Lean Prediction`,
      color='orange'
    ),
  )+
  theme_bw()+
  scale_color_discrete(
    name = "Y series", 
    labels = c("Ground Truth", "Large Model","Small Model","Lean Model")
  )+
  labs(
    x="Patient ID",
    y="Stroke 1=Yes"
  )

ggplotly(plt)

@@

## Confusion Matrix and Model Statistics

### Large Predictions
```{r}
confusionMatrix(
  predictions$`Large Prediction`,
  as.factor(stroke_factor_testing_data$stroke),
  positive = "1", 
  dnn=c("Prediction", "Actual"), 
  mode = "everything"
)

@@

Extremely low kappa

### Small Predictions
```{r}
confusionMatrix(
  predictions$`Small Prediction`,
  as.factor(stroke_factor_testing_data$stroke),
  positive = "1", 
  dnn=c("Prediction", "Actual"), 
  mode = "everything"
)

### Lean Predictions
```{r}
confusionMatrix(
  predictions$`Lean Prediction`,
  as.factor(stroke_factor_testing_data$stroke),
  positive = "1", 
  dnn=c("Prediction", "Actual"), 
  mode = "everything"
)

```
Y axis is ground truth, x axis is predictions

@@

## ROC Curve
```{r}

stroke_rf_predictions = as.tibble(as.numeric(as.character(stroke_rf$votes[,2])))
stroke_rf_actual = tibble(as.factor(stroke_factor_training_data$stroke))

stroke_prediction_comparison = prediction(
  stroke_rf_predictions,
  stroke_rf_actual,
)

stroke_rf_performance = performance(
  stroke_prediction_comparison,
  measure = "tpr",
  x.measure = "fpr"
)

stroke_rates = 
  data.frame(
    fp = stroke_prediction_comparison@fp,  #<- false positive classification.
    tp = stroke_prediction_comparison@tp,  #<- true positive classification.
    tn = stroke_prediction_comparison@tn,  #<- true negative classification.
    fn = stroke_prediction_comparison@fn
  )
colnames(stroke_rates) = c("fp", "tp", "tn", "fn")

tpr = stroke_rates$tp /(stroke_rates$tp + stroke_rates$fn)
fpr = stroke_rates$fp /(stroke_rates$fp + stroke_rates$tn)
```

```{r}
# plot
plot(fpr,          #<- x-axis value.
     tpr,          #<- y-axis value.
     col = "blue",  #<- color of the line. 
     type = "l")   #<- line type.
abline(0,1)
grid(col = "black")
```
